\textbf{EECS 340: Assignment 2}

### 2020-02-04 assignment_2/article.tex
💄 Fix language and expressions.

\author{Shaochen (Henry) ZHONG, \inlinecode{sxz517} \\ Zhitao (Robert) CHEN, \inlinecode{zxc325}}
\date{Due and submitted on 02/03/2020 \\ EECS 340, Dr. Koyutürk}
\maketitle

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(a) $max\{f(n), g(n)\} = \Theta (f(n) + g(n))$}

@@

Since both the $O$- and $\Omega$-notation are established, we may therefore conclude:

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(b1) $f(n) + d = O(f(n))$.}

@@

For the seek of disambiguation, we rewrite the questioned equation as $f(n) + d = O(f(n))$ by $d$ replacing $c$ for $d > 0$.

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(b2) If $f(n) \geq 1$, then $f(n) + d = O(f(n))$.}

For the seek of disambiguation, we rewrite the questioned equation as $f(n) + d = O(f(n))$ by $d$ replacing $c$ for $d > 0$.

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(c1) If $f(n) = O(g(n)), \log(f(n)) \geq 0$ and $\log(g(n)) \geq 0$, then $log(f(n)) = O(\log(g(n))$.}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(c2) If $f(n) = O(g(n)), \log(f(n)) \geq 0$ and $\log(g(n)) \geq 1$, then $log(f(n)) = O(\log(g(n))$.}

According to the defination of $O$-notation, we must have:

@@

For the seek of disambiguation, we rewrite the questioned equation as: if $f(n) = O(n^k)$, then $f(2n) = O(n^k)$ by $k$ replacing $c$ for $k > 0$.

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(d3) If $f(n) = \Theta(n^k)$, then $f(2n) = \Theta(f(n))$}

For the seek of disambiguation, we rewrite the questioned equation as: if $f(n) = \Theta(n^k)$, then $f(2n) = \Theta(f(n))$.

@@

The above equations can be rewrite as:

@@

Where all of them can be generalized as $\Theta(\log(n))$, as it is known that $n^\epsilon \leq bn \leq n^a$ due to the decending of \textit{power(s)}.

The relationship of the above expressions with $\log_{\frac{1}{\epsilon}}(n)$ can be a bit unintuitive, we may show they are considered equivalent with:
\begin{gather}
    \lim\limits_{n \to \infty} \frac{\log(n^\epsilon)}{\log_{\frac{1}{\epsilon}}(n)} = \lim\limits_{n \to \infty} \frac{\epsilon \log_{2}n}{\frac{\log_{2}n}{\log_{2}(\frac{1}{\epsilon})}} = \lim\limits_{n \to \infty} \epsilon \log_2(\frac{1}{\epsilon}) = c \nonumber\\
    \Rightarrow \log(n^\epsilon) \equiv \log_{\frac{1}{\epsilon}}(n)
\end{gather}

@@

Considered $ \log(n)$ is a generalized form of the perivous group of functions,  $(\log (n))^a$ is proven to be greater than the perivous group.

@@

The above equations can be rewrite as:
\begin{gather}
    a^{\log_a(n)} = n^1 = \Theta(n) \\
    \epsilon n = \Theta(n) \\
    \frac{n}{a} = \frac{1}{a}n =  \Theta(n)
\end{gather}

@@

These are all polynomial functions with greatest power $> 1$, thus they are considered greater than the previous group (functions with greatest power $= 1$), and ordered according to ascending of \textit{power(s)}.

>>>>

\author{Shaochen (Henry) ZHONG, \inlinecode{sxz517} \\ Zhitao (Robert) CHEN, \inlinecode{zxc325}}
\date{Due and submitted on 02/03/2020 \\ EECS 340, Dr. Koyut{\"u}rk}
\maketitle

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(a) $max\{f(n), g(n)\} = \Theta (f(n) + g(n))$}
\textbf{True}

@@

Since both the $O$- and $\Omega$-notations are established, we may therefore conclude:

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(b1) $f(n) + d = O(f(n))$}

@@

For the sake of disambiguation, we rewrite the questioned equation as $f(n) + d = O(f(n))$ by $d$ replacing $c$ for $d > 0$.

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(b2) If $f(n) \geq 1$, then $f(n) + d = O(f(n))$}
\textbf{True}

For the sake of disambiguation, we rewrite the questioned equation as $f(n) + d = O(f(n))$ by $d$ replacing $c$ for $d > 0$.

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(c1) If $f(n) = O(g(n)), \log(f(n)) \geq 0$ and $\log(g(n)) \geq 0$, then $log(f(n)) = O(\log(g(n))$}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(c2) If $f(n) = O(g(n)), \log(f(n)) \geq 0$ and $\log(g(n)) \geq 1$, then $log(f(n)) = O(\log(g(n))$}
\textbf{True}

According to the definition of $O$-notation, we must have:

@@

\textbf{True}

For the sake of disambiguation, we rewrite the questioned equation as: if $f(n) = O(n^k)$, then $f(2n) = O(n^k)$ by $k$ replacing $c$ for $k > 0$.

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(d3) If $f(n) = \Theta(n^k)$, then $f(2n) = \Theta(f(n))$}
\textbf{True}
For the sake of disambiguation, we rewrite the questioned equation as: if $f(n) = \Theta(n^k)$, then $f(2n) = \Theta(f(n))$.

@@

The above equations can be losely rewritten as:

@@

Where all of them can be generalized as $\Theta(\log(n))$, as it is known that $n^\epsilon \leq bn \leq n^a$ due to the decending of \textit{power(s)}.\newline

Note the relationship of the above expressions with $\log_{\frac{1}{\epsilon}}(n)$ can be a bit unintuitive, we may show they are considered equivalent with:
\begin{gather}
    \lim\limits_{n \to \infty} \frac{\log(n^\epsilon)}{\log_{\frac{1}{\epsilon}}(n)} = \lim\limits_{n \to \infty} \frac{\epsilon \log_{2}n}{\frac{\log_{2}n}{\log_{2}(\frac{1}{\epsilon})}} = \lim\limits_{n \to \infty} \epsilon \log_2(\frac{1}{\epsilon}) = c \nonumber\\
    \Rightarrow \log(n^\epsilon) \equiv \log_{\frac{1}{\epsilon}}(n)
\end{gather}

@@

Considered $ \log(n)$ is a generalized form of the previous group of functions,  $(\log (n))^a$ is proven to be greater than the previous group.

@@

The above equations can be losely rewritten as:
\begin{gather}
    a^{\log_a(n)} = n^1 = \Theta(n) \\
    \epsilon n = \Theta(n) \\
    \frac{n}{a} = \frac{1}{a}n =  \Theta(n)
\end{gather}

@@

These are all polynomial functions with the greatest power $> 1$; thus they are considered greater than the previous group (functions with the greatest power $= 1$), and ordered according to ascending of \textit{power(s)}.
